Noisy Work: A Review of The Uncertainty Visualisation Literature

### 2024-03-31 paper.qmd
small re-wording of last intro paragraph

The review provided here attempts to address these issues. We begin with understanding the definition problem, to obtain and understanding of the *purpose* of visualising uncertainty, and understand if the current visualisation tools are sufficient to achieve that purpose and if not, where there is need for new methodology. We also posit that "uncertainty visualisation" is too diffuse to be considered a field in itself, but rather should be dissected into smaller components. The ideal role of this review is to provide a guide for research in these topics, to help synthesize this noisy field. <!-- XXX Its not clear that these last two sentences are helpful here.--> <!-- In understanding this purpose, we will also consider whether or not "uncertainty visualisation" is a valid sub-field of visualisation itself, or if that distinction has only arisen as a by product of the confused definition of uncertainty. Ultimately, this paper should serve as a guide for future uncertainty visualisation authors to prevent their work from becoming noise in what is already an incredibly noisy field.-->

>>>>

The review provided here attempts to address these issues. We begin with understanding the definition problem, to obtain and understanding of the *purpose* of visualising uncertainty, and understand if the current visualisation tools are sufficient to achieve that purpose and if not, where there is need for new methodology. We also posit that "uncertainty visualisation" is too diffuse to be considered a field in itself, but rather should be dissected into smaller elements. The ideal role of this review to help synthesize this noisy field, by collecting together essential components, summarising different viewpoints the current literature, and provide a guide for potential research topics. <!-- In understanding this purpose, we will also consider whether or not "uncertainty visualisation" is a valid sub-field of visualisation itself, or if that distinction has only arisen as a by product of the confused definition of uncertainty. Ultimately, this paper should serve as a guide for future uncertainty visualisation authors to prevent their work from becoming noise in what is already an incredibly noisy field.-->
